\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

%\TODO{review and summarize this part}
%\TODO{CHECK FOR MAXIMUM 250 WORDS!}

\TODO{REVIEW}


% problem

A system was developed for the creation of urban scenarios produced on large screen displays
using laser pointers as input devices and supporting collaborative usage.
A novel interface had to be developed to support interaction with such input devices,
based on the concept of gates and circular menus with a non-intrusive interface.


% implementation / features

Users can navigate on a virtual world using a set of comprehensive navigation modes, namely:
first person, bird's eye view and examine modes, along with a multimodal flight mode.
Simple shapes can be created and modeled using a minimalistic set of modeling tools.
Buildings can be instantiated from a library of facade styles by drawing
the desired blueprint and setting the facade height to generate unique buildings.
Buildings and other shapes can also be transformed and cloned.
Objects in the scene can have notes attached to them to aid in reviewing sessions.
In order to increase the available building possibilities, styles are defined using a dedicated XML grammar
specifying the walls and roof types along with the spatial distribution of its facade attachments.
An alternative building creation work flow is proposed to take advantage of this system for early prototypes
and showcasing projects.

The system architecture is described throughly, followed by implementation details and evaluation tests.
It is shown that users could successfully make use of the offered features based on a stroke-based
interface and set of comprehensive menus. 
The project conclusions and future work close this document.


% results

%\TODO{TESTS AND CONCLUSION}



%The context and objectives of the project are defined at the introduction.
%Related work is then commented, followed by the analysis of the problem.
%Concepts, tasks and interface are then designed, with their implementation following.
%Evaluation of the system and conclusions end the paper.

%\TODO{CHECK FOR 4 -- 6 KEYWORDS!}
\textbf{Keywords:} architecture prototype, facade, stroke, building, multimodal interface, navigation, reviewing, large screen display, collaboration, shape modeling
